---
title: "simulation"
author: "Yuqi Miao"
date: "10/31/2019"
output:
  html_document:
    toc: true
    toc_float: true
---


```{r}
library(tidyverse)
set.seed(1)
```

```{r}
sim_regression = function(n,beta0 = 2, beta1 = 3){
    sim_data = tibble(
        x = rnorm(n, mean = -4, sd = 1),
        y =  beta0 + beta1 * x + rnorm(n, 0, 1)
    )
    
     ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}
```

# rerun using for loop
different from map, 
  for map, we are using this function to a dataframe, 
  but simulation needs to generating data of certain amount under a specific rule and get the new dataframe
```{r}
output = vector("list", length = 500)
for (i in 1:500) {
    output[[i]] = sim_regression(n = 30)
}
bind_rows(output) %>% 
    ggplot(aes(x = beta0_hat)) + geom_density()
    

```



## rerun simulation using `purrr`

```{r}
output <- rerun(500,sim_regression(n = 30))
## equals to the former for loop, give the results in list format, separated by times 

bind_rows(output) %>% 
    ggplot(aes(x = beta0_hat)) + geom_density()
## bind_rows == rbind_list() and rbind_all() 


sim_results = 
  rerun(100, sim_regression(30, 2, 3)) %>% 
  bind_rows() ## always remember to use bind_rows!
 
sim_results %>% 
    ggplot(aes(x = beta0_hat, y = beta1_hat)) + 
    geom_point()


### x 取值于 mean = 0 & mean = 1 normal distribution, huge difference!
### beta0_hat和beta1_hat 本身就有线性关系， x均值等于0的时候相乘得零只剩随机误差， x均值越大，线性关系越明显

```


```{r}
sim_results %>% 
  pivot_longer(cols = beta0_hat:beta1_hat, names_to = "parameter", values_to = "estimate") %>% 
  # == gather(key = parameter, value = estimate, beta0_hat:beta1_hat) %>% 
  group_by(parameter) %>% 
  summarize(emp_mean = mean(estimate),
            emp_var = var(estimate)) %>% 
  knitr::kable(digits = 3)
```


# Simulation: SLR for several ns


```{r}
n_list = list(
    "n_30" = 30,
    "n_60" = 60,
    "n_120" = 120,
    "n_240" = 24
    
)

output = vector("list",length = 4)

for (i  in 1:4) {
    output[[i]] = rerun(100, sim_regression(n = n_list[[i]])) %>% 
        bind_rows
    
}

output
g_output <- vector("list",length = 4)
for (i in 1:4) {
  g_output[[i]] <-  
    output[[i]] %>% 
      ggplot(aes(x = beta0_hat))+geom_density()
  
}
output[[4]] %>% 
    ggplot(aes(x = beta0_hat))+geom_density()  
## sample size bigger,more approximate to normal distribution
g_output[[4]]
```



## when to bind_rows??

every results from sim_regression is a dataframe with a sample size, so for every sample size, we need to use bind_rows to intergrate the coefficient with same sample size into one dataframe, so our final datafrome would have only 4 rows and 1 columns containing the coresponding coefficient dataframe.

```{r}
sim = 
  tibble(
    size = seq(30,120,by = 30)
  ) %>% 
  mutate(
    estimates_list = map(.x = size,.f = ~rerun(100,sim_regression(n = .x))),
    estimates = map(.x = estimates_list, ~bind_rows(.x))
  ) %>% 
  select(-estimates_list) %>% 
  unnest(estimates) %>% 
  pivot_longer(
    cols = beta0_hat:beta1_hat,
    names_to = "parameters",
    values_to = "estimates"
  )
sim %>%  
  filter(parameters == "beta1_hat") %>% 
  ggplot(aes(x = estimates)) + 
  geom_density() +
  facet_grid(.~size)

sim %>% 
  group_by(parameters, size) %>% 
  summarize(sd = sd(estimates),mean = mean(estimates))
```


## intergration
```{r}
sim_results <- 
    tibble(
        sample_size = c(30,60,120,240),
        output_list = map(.x = sample_size, ~rerun(100, sim_regression(n = .x))),
        output_df= map(output_list, bind_rows)
    
) %>% 
    select(-output_list) %>% 
    unnest(output_df)

```



```{r}
sim_results %>% 
    group_by(sample_size) %>% 
    summarise(var_b1 = var(beta0_hat))
```


```{r}

sim_results %>% 
    mutate(
        sample_size = str_c("n = ",sample_size),
        sample_size = fct_inorder(sample_size)
    ) %>% 
    ggplot(aes(x = beta0_hat, y =beta1_hat)) +
    facet_grid(.~sample_size)+
    geom_violin()
```


```{r}
sim_results %>% 
  pivot_longer(
    beta0_hat:beta1_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter, sample_size) %>% 
  summarize(emp_mean = mean(estimate),
            emp_var = var(estimate)) %>% 
  knitr::kable(digits = 3)
```

